% DOCUMENT FORMATING
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% PACKAGES
\usepackage{amsmath} % For extended formatting
\usepackage{amssymb} % For math symbols
\usepackage{amsthm} % For proof environment
\usepackage{array} % For tables
\usepackage{enumerate} % For lists
\usepackage{extramarks} % For headers and footers
\usepackage{fancyhdr} % For custom headers
\usepackage{graphicx} % For inserting images
\usepackage{multicol} % For multiple columns
\usepackage{verbatim} % For displaying code
\usepackage{tkz-euclide}
\usepackage{pgfplots}
\usepackage{mathtools}


% SET UP HEADER AND FOOTER
\pagestyle{fancy}
\lhead{\MyCourse} % Top left header
%\chead{\MyTopicTitle} % Top center header
\rhead{\MyAssignment} % Top right header
%\lfoot{\MyCampus} % Bottom left footer
\cfoot{} % Bottom center footer
%\rfoot{\MySemester} % Bottom right footer
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand\footrulewidth{0.4pt} % Size of the footer rule




% ----------
% TITLES AND NAMES 
% ----------

\newcommand{\MyCourse}{Math 241}
\newcommand{\MyAssignment}{Section 3.7 Optimization}
%\newcommand{\MySemester}{Spring 2020}
%\newcommand{\MyCampus}{University of Hawaii at Manoa}

% ----------
% BEGIN DOCUMENT
% ----------

\begin{document} 
\begin{enumerate}
\item A farmer has 2400 ft. of fencing and wants to fence off a rectangular field that borders a straight river. He needs no fencing along the river. What are the dimensions of the field that has the largest area?

\pagebreak

\item A cylindrical can is to be made to hold 1 L of oil. Find the dimensions that minimize the cost of the metal to manufacture the can.

\pagebreak
\item Find the largest rectangle that can be inscribed in a semicircle of radius $r$.

\pagebreak
\item An open top box is to be made from a 2 box a 24 in. by 36 in. piece of cardboard by removing a square from each corner of the box and folding up the flaps on each side. What size square should be cut out to each corner to get a box with maximum volume?

\pagebreak
\item A rectangular box with a square base, an open top and a volume of 216 $\text{m}^3$ is to be constructed. What should the dimensions be to minimize the surface area of the box? What is the minimum surface area?

\pagebreak
\item A rectangular box has a base that is a square. The perimeter of the base plus the height of the box is equal to 3 feet. What is the largest possible volume for such a box, and what are its dimensions? Use Calculus to justify your answer.

\pagebreak
\item A power line needs to be run from a power station located on a beach to an offshore facility underwater located 5000 ft east and 1000 ft north. It costs \$ 50/ ft to run a power line on land and \$ 130/ ft to run the power line under water. How much of the power line should be run along the land to minimize the overall cost? What is the minimal cost?
\end{enumerate}
\end{document}