\documentclass[12pt]{article}
\usepackage{url}
\textwidth=7in
\textheight=9.9in
\topmargin=-1.8in
\headheight=.5in
\headsep=.5in
\hoffset  -1in
\usepackage{hyperref}

\pagestyle{empty}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\begin{document}

\begin{center}
{\bf MATH 241 SECTIONS 03 \& 04 \ \ FALL 2024 \\
\textbf{Lecture}: MWF 10:23am-11:20am\quad\quad\textbf{Room}: Keller 302\\
\textbf{Recitation (Section 3):} T 9:30am-10:20am\quad\quad\textbf{Room}: KEL 404\\
\textbf{Recitation (Section 4):} T 8:30am-9:20am\quad\quad\textbf{Room}: KEL 404}
\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}



\renewcommand{\arraystretch}{2}

\vskip.2in
\noindent\textbf{Instructor:} Julian Hachmeister

\noindent\textbf{Email:} julianh@hawaii.edu

\noindent\textbf{Office:} Keller Hall 409

\noindent\textbf{Office Hours:} MWF 11:30-12:30\\

\noindent\textbf{Teaching Assistant:} Kawika O'Connor, oconnor3@hawaii.edu\\
\noindent\textbf{Learning Assistants:} \\

\hspace{0.1in} \textbf{Section 3:} \quad Zoe Webster, zwebster@hawaii.edu\quad\quad Trevor Sanger, sangert@hawaii.edu\\

\hspace{0.1in} \textbf{Section 4:} \quad Zoe Webster, zwebster@hawaii.edu\quad\quad Hannah McKay, hmckay@hawaii.edu\\

\noindent\textbf{Textbook:} \emph{Calculus} by James Stewart, eighth edition.\\ 
This is often bundled with an access code for WebAssign which you will need as we will be using WebAssign for online homework. The university bookstore has physical (loose-leaf) copies of the book bundled with a WebAssign access code. Purchasing through the Cengage website will bundle an electronic version of the book with WebAssign access. The bookstore copy comes bundled with multi-semester access to WebAssign.
\vskip .2in

\noindent\textbf{Course description:}
Basic concepts, differentiation with applications, integration.

\vskip.2in
\noindent\textbf{Pre-requisites:} A grade of C or better in Math 140 or Math 215 or precalculus assessment as specified by the department.

\vskip.2in
\noindent\textbf{(Tentative) Schedule:} A spreadsheet with a proposed schedule can be found on Laulima or by using the link below. I will try to stick to this schedule, but we may deviate as needed.

%ADD LINK LINK TO THE SCHEDULE
\begin{center}
    \href{https://docs.google.com/spreadsheets/d/1TdVJNadHgSydFqxXtTEkET8og4EhJUvnUNqrxa_NcTA/edit?usp=sharing}{Google Drive link for schedule}
\end{center}


\noindent\textbf{Lecture}: You are encouraged to attend class as the homework will come directly from the lecture. In case of an absence, you will need to ask a fellow student for notes.

\vskip.2in

\noindent\textbf{Homework}: WebAssign (online) homework will be assigned after each class and due two days later by midnight. For example, homework assigned on Monday will be due at midnight on Wednesday. \textbf{No late work will be accepted.} Information on enrolling in WebAssign will be on the course Laulima website. 

\vskip.2in

\noindent\textbf{Recitation, Quizzes, and Worksheets}: Our recitation meets once a week on Tuesday. A short quiz will be given at the beginning covering material from the previous week's recitation worksheet. The remainder of the class will be spent completing a worksheet. Your worksheet grade will be based on your active participation during recitation.

\pagebreak

\noindent\textbf{Midterms:} We will have two midterms throughout the semester and a final. The dates are 

\begin{center}
\begin{tabular}{llll}
    &(10/09) Midterm 1  &6:00pm-7:15pm &Room TBA\\
    &(11/20) Midterm 2 &6:00pm-7:15pm &Room TBA\\
    &(12/18) Final Exam &12:00pm - 2:00pm &Room TBA
\end{tabular}
 \end{center}

The final exam will be cumulative. 

Attendance on these dates is compulsory.  Any student who has an excused, documented conflict with a test date/time must inform their instructor \textbf{within the first two weeks of the semester} when possible and take a make-up exam no later than one week of the original date above. Late requests will either be denied or will result in an automatic deduction from the exam score. Under no circumstances will the final exam be given before the date above.

\vskip 0.2in

\noindent\textbf{Grade Breakdown:} A curve, if applied, will be to the final exam.

\begin{center}

Quizzes: 10\%

Worksheets: 10\%

Homework: 10\%

Midterms: 40\%

Final: 30\%

\end{center}

\vskip.2in
\noindent\textbf{Calculators}: Calculators are never allowed on exams or quizzes. If I feel a student has been using any kind of technology on an exam or quiz, they will receive a 0 score for that exam/quiz.

\vskip.2in
\noindent\textbf{Late work policy:} Students who are enroll in the class after the first day will be required to make up any missing material no later than two weeks after their enrollment date. Otherwise, no late work will be accepted unless in the case of an emergency. This is left to my discretion.

\vskip .2in

\noindent\textbf{Out-of-Class Work:} For a 4-Credit-Hour course, you are expected to spend at least 8 hours each week outside of class and recitations on work related to this course.

\vskip.2in
\noindent\textbf{Academic Honesty}:  As a University of Hawaii student, you have agreed to abide by the University's academic  policy.

\vskip.2in

\noindent\textbf{Getting Help:} If you feel you are falling behind in class or not understanding the material, please contact me as soon as possible.  It can be discouraging to fall behind, and it's difficult to get caught up if you let it go too long.  The best way to reach me is by email and you are encouraged to attend office hours. 

\vskip.2in
\noindent\textbf{ Attendance Policy}:  Students are expected to attend classes regularly.

\vskip.2in
\noindent\textbf{KOKUA:} Any student who feels they may need an accommodation based on the impact of a disability is invited to contact me privately. I would be happy to work with you, and the KOKUA Program (Office for Students with Disabilities) to ensure reasonable accommodations in my course. KOKUA can be reached at (808) 956-7511 or (808) 956-7612 (voice/text) in room 013 of the Queen Lili'uokalani Center for Student Services. More information can be found at their website at https://www.hawaii.edu/kokua/

\end{document}